Integration of national demographic-disturbance relationships into local caribou population viability projections can reduce uncertainty and inform monitoring decisions

### 2024-10-17 analysis/paper/paper.Rmd
save pdfs in figs_submit folder and name according to figure number

for(f in figSet){
  if(f =="EVPIall"){addBit=""}else{addBit=resultSet}
  currentFile = here::here(paste0("figs/",resultScenario,"/",f,addBit,".png"))
  newFile = here::here(paste0("figs/forPaper/",f,addBit,".png"))
  file.copy(currentFile, newFile,overwrite=T)
}
```

@@

```{r figDisturbance, fig.cap=".", cache=TRUE}
knitr::include_graphics(here::here("figs/forPaper/distScnscmult6ay1aSf1.png"))

```

```{r exampleTrajectories, fig.cap=".", cache=TRUE}
knitr::include_graphics(here::here("analysis/paper/figs/DemographicRates.png"))

```

```{r examplePredictions, fig.cap=".", cache=TRUE}

knitr::include_graphics(here::here("analysis/paper/figs/bayesianModelExamples.png"))
```

```{r figDiffs, fig.cap=".", cache=TRUE}
knitr::include_graphics(here::here("figs/forPaper/diffscmult6ay1aSf1.png"))
```

```{r figStatusErrors, fig.cap=".", cache=TRUE}
knitr::include_graphics(here::here("figs/forPaper/powercmult6ay1aSf1.png"))
```

```{r figEVSI, fig.cap=".", cache=TRUE}

knitr::include_graphics(here::here("figs/forPaper/EVSIcmult6ay1aSf1.png"))
```

>>>>

for(f in figSet){
  if(f =="EVPIall"){addBit=""}else{addBit=resultSet}
  currentFile = here::here(paste0("figs/",resultScenario,"/",f,addBit,".png"))
  newFile = here::here(paste0("figs/forPaper/",f,addBit,".png"))
  file.copy(currentFile, newFile,overwrite=T)

  currentFile = here::here(paste0("figs/",resultScenario,"/",f,addBit,".pdf"))
  newFile = here::here(paste0("analysis/paper/figs_submit/",f,addBit,".pdf"))
  file.copy(currentFile, newFile,overwrite=T)
}
```

@@

```{r figDisturbance, fig.cap=".", cache=TRUE}
knitr::include_graphics(here::here("figs/forPaper/distScnscmult6ay1aSf1.png"))
file.rename(here::here("analysis/paper/figs_submit/distScnscmult6ay1aSf1.pdf"), 
            here::here("analysis/paper/figs_submit/Figure1_distScnscmult6ay1aSf1.pdf"))
```

```{r exampleTrajectories, fig.cap=".", cache=TRUE}
knitr::include_graphics(here::here("analysis/paper/figs/DemographicRates.png"))
file.rename(here::here("analysis/paper/figs_submit/DemographicRates.pdf"), 
            here::here("analysis/paper/figs_submit/Figure2_DemographicRates.pdf"))
```

```{r examplePredictions, fig.cap=".", cache=TRUE}
knitr::include_graphics(here::here("analysis/paper/figs/bayesianModelExamples.png"))
file.rename(here::here("analysis/paper/figs_submit/bayesianModelExamples.pdf"), 
            here::here("analysis/paper/figs_submit/Figure3_bayesianModelExamples.pdf"))
```

```{r figDiffs, fig.cap=".", cache=TRUE}
knitr::include_graphics(here::here("figs/forPaper/diffscmult6ay1aSf1.png"))
file.rename(here::here("analysis/paper/figs_submit/diffscmult6ay1aSf1.pdf"), 
            here::here("analysis/paper/figs_submit/Figure4_diffscmult6ay1aSf1.pdf"))
```

```{r figStatusErrors, fig.cap=".", cache=TRUE}
knitr::include_graphics(here::here("figs/forPaper/powercmult6ay1aSf1.png"))
file.rename(here::here("analysis/paper/figs_submit/powercmult6ay1aSf1.pdf"), 
            here::here("analysis/paper/figs_submit/Figure5_powercmult6ay1aSf1.pdf"))
```

```{r figEVSI, fig.cap=".", cache=TRUE}
knitr::include_graphics(here::here("figs/forPaper/EVSIcmult6ay1aSf1.png"))
file.rename(here::here("analysis/paper/figs_submit/EVSIcmult6ay1aSf1.pdf"), 
            here::here("analysis/paper/figs_submit/Figure6_EVSIcmult6ay1aSf1.pdf"))
```
